A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-07-16 paper/paper.tex
Moving table nu-sets above

\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets. To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\hexagon$.

@@

so that the following holds.

\begin{table}[H]
  \centering
  \begin{tabularx}{0.7\linewidth}{X|X|X}
    \toprule
    Value of $\nu$ & 1                               & 2                  \\
    \graymidrule
    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
    \bottomrule
  \end{tabularx}
\end{table}

>>>>

\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets obtained by building on an arbitrary alphabet $\nu$, so that the following holds:

\begin{table}[H]
  \centering
  \begin{tabularx}{0.7\linewidth}{X|X|X}
    \toprule
    Cardinal of $\nu$ & 1                               & 2                  \\
    \graymidrule
    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
    \bottomrule
  \end{tabularx}
\end{table}

To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\hexagon$.

@@
